Synthesis of Solar Photovoltaic Systems: Optimal Sizing Comparison\thanks{Supported by Newton Fund (ref. 261881580) and FAPEAM (Amazonas State Foundation for Research Support, calls 009/2017 and PROTI Pesquisa 2018).}

### 2020-01-21 Tex/CAV2019/Trindade_Cordeiro_CAV2020.tex
revised Section 5
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

%---------------------------------------------------------------------------
\section{Results and Discussion}
%---------------------------------------------------------------------------
%---------------------------------------------------------------------------
\subsection{Description of the Case studies}
%---------------------------------------------------------------------------
The proposed synthesis approach was evaluated in  seven stand-alone PV system case studies: 
\textbf{case study 1:} power peak: 342 W, power surge: 342 W, energy consumption: 3,900 Wh/day, battery autonomy: 48 h; \textbf{case study 2:} Power peak: 814 W, power surge: 980 W, energy consumption: 4,880 Wh/day, battery autonomy: 48 h; \textbf{case study 3:} power peak: 815 W, power surge: 980 W, energy consumption: 4,880 Wh/day, battery autonomy: 12 h; \textbf{case study 4:} power peak: 253 W, power surge: 722 W, energy consumption: 3,600 Wh/day, battery autonomy: 48 h; \textbf{case study 5:} power peak: 263 W, power surge: 732 W, energy consumption: 2,500 Wh/day, battery autonomy: 48 h; \textbf{case study 6:} power peak: 322 W, power surge: 896 W, energy consumption: 4,300 Wh/day, battery autonomy: 48 h; \textbf{case study 7:} power peak: 1,586 W, power surge: 2,900 W, energy consumtion: 14,000 Wh/day, battery autonomy: 48 h.

These case studies were defined based on the usual electrical load found in riverside communities in the State of Amazonas,  Brazil~\cite{TrindadeCordeiro19,Agrener2013}, with the exception of case 7, that was idealized as a small town solution to support a few lamps and a 12 kBTUs air-conditioner. For all cases, an estimated load curve (kWh) was defined based on the electronics consumers in each house. Our synthesis algorithm was fed with data and costs of forty equipment items from ten different manufacturers of PV systems.

@@

All experiments regarding the verification tools were conducted on an otherwise idle Intel Xeon CPU E5-4617 ($8$-cores) with $2.90$ GHz and $64$ GB of RAM, running Ubuntu $16.04$ LTS $64$-bits. For HOMER Pro, we have used an Intel Core i5-$4210$ ($4$-cores) with $1.7$ GHz and $4$ GB of RAM running Windows 10. \textcolor{red}{The hardware platform was not the same because of the availability of the machines, and this has impact in respect to the performance that is less favorable to HOMER Pro}. We perform the experiments with a predefined time out of $240$ minutes.

%---------------------------------------------------------------------------
\subsection{Results}
%---------------------------------------------------------------------------
A Table with the details of the results is present on-line\footnote{\url{https://drive.google.com/file/d/1I1Cg4FNz9grMqXHUmOKnd-\_PFmLpmk6m/view?usp=sharing}}.

Related to the verifiers comparison, CPAchecker was able to synthesize the optimal sizing in six out of seven case studies (cases $1$ to $6$): CPAchecker produced the results within the time limit, which varied from $2.24$ to $3.92$ hours. Only case study $7$ led to a \textit{time out} result in CPAchecker, i.e., it was not solved within $240$ minutes. The violation (SAT result) indicated in on-line Table is the $assert$ of Line $22$ at Algorithm~\ref{alg:verification-algorithm}. CBMC and ESBMC are unable to produce any conclusive result. Situations of \textit{time out} or \textit{out of memory} occurred; these results partially answer the \textit{EG1} and \textit{EG2}, \textcolor{red}{because there are optimal solutions and CPAchecker presented the better comparative results among the verifiers}.

@@

For the inverters, HOMER Pro suggests a value in kW very close to the peak of every case study, and it is just a reference value and not a commercial value of the employed inverter. The proposed synthesis tool, however, presents inverters that are commercial and can be found off-the-shelf. Therefore, this feature is a PRO to the formal synthesis method. Concerning the charge controllers, HOMER Pro does not include it as an explicit equipment in its mathematical model, only the synthesis tool presents a commercial controller and includes it during the cost analysis. Therefore, the formal synthesis method presents more reliable results than HOMER Pro. Case study $7$ was not solved by the synthesis tool within the time limit established during the experimental phase. HOME Pro was unable to simulate case study $3$ since it does not have the feature of adjusting the battery autonomy, i.e., the tool always tries to feed with electricity the given load during $365$ days/year. \textcolor{red}{This lack of recourse is a limitation, because it is usual to establish the autonomy as a design requirement}.

In terms of performance, HOMER Pro was able to evaluate six case studies (cases $1$, $2$, $4$, $5$, $6$, and $7$) within a time shorter than $30$ seconds, which was faster than the proposed automated synthesis tool (cf.~\textit{EG3}) \textcolor{red}{but not so sound as our synthesis method}.

\textcolor{red}{Comparing the results between the formal synthesis with CPAchecker and HOMER Pro, we have observed that the cost was very close in cases $1$, $4$, $5$ and $6$, with difference varying from $0.23$\% to $17.4$\%. However, HOMER Pro does not use costs related to charge controllers, which were introduced into our synthesis model. This charge controller cost makes the synthesis approach more precise and real. It was observed that there exists a divergence in case study $2$, where the costs presented by HOMER Pro were $54$\% higher than our synthesis tool. However this case study does not have a deployed PV system in order to validate which result is the correct.}

@@

%------------------------------------
\section{Conclusion} 
%------------------------------------
\textcolor{red}{
Our novelty relies on a practical approach for to pursuit of the optimal solution of PV systems using formal methods. The use of formal synthesis has no precedent in literature, and we show that the results of our approach, using seven case studies, are promising.} 
%\textcolor{red}{What is the novelty of our work? what are the impacts/relevance of our method to the society and formal methods community? How formal methods can improve the people's life? we should emphasize the relevance of the problem we solve and give numbers to show the efficiency of our approach if compared to HOME Pro.}
Our synthesis tool can present a solution, which is far detailed and closer to the commercial reality than the solution presented by HOMER Pro, an state-of-the art simulation tool. The use of data from real deployed systems in Amazonas State, Brazil, were important in order to reach that conclusion. The battery autonomy feature of our synthesis approach is an advantage as well. In addition, our automated synthesis method can provide all the details of every component of a PV system solution, with complete electrical details from datasheet of manufacturers, including the model of the component, nominal current, and voltage. These details are important for the owner of the system and aids the process of equipment purchase.
%
% ---- Bibliography ----
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%
\bibliographystyle{splncs04}
\bibliography{trindadeThesis}
%
\end{document}
%\subsection{Design and Simulation of Solar PV systems}
%The design and validation of a PV system can be done by hand or with the aid of a software tool. In order to address different aspects of the PV system design, there are various software tools available in the literature~\cite{Rajanna,Rawat}.
%public domain and commercial software available for the PV market. 
%According to \cite{Brooks}, t
%%%%%%%%%%
%
%The capabilities of tools available in the literature range from simple solar resource and %energy production estimation, %to site survey and system design tools,
%to complex financial analysis and project optimization. At this study, the commercial simulation tool HOMER PRO was selected to be used at the case studies in order to be compared with the automated verification tools.

>>>>

%---------------------------------------------------------------------------
\section{Results and Discussion}
%---------------------------------------------------------------------------
%---------------------------------------------------------------------------
\subsection{Description of the Case Studies}
%---------------------------------------------------------------------------

The proposed synthesis approach was evaluated in seven stand-alone PV system case studies. Here we report each case study as a tuple \textit{\{power peak (W); power surge (W); energy consumption (Wh/day); battery autonomy (hours)\}} as follows:
\textbf{case study 1:} \{342; 342; 3,900; 48\}; \textbf{case study 2:} \{814; 980; 4,880; 48\}; \textbf{case study 3:} \{815; 980; 4,880; 12\}; \textbf{case study 4:} \{253; 722; 3,600; 48\}; \textbf{case study 5:} \{263; 732; 2,500; 48\}; \textbf{case study 6:} \{322; 896; 4,300; 48\}; \textbf{case study 7:} \{1,586; 2,900; 14,000; 48\}.
These case studies were defined based on the usual electrical load found in riverside communities in the State of Amazonas, Brazil~\cite{TrindadeCordeiro19,Agrener2013}, except for case 7, which was idealized as a small-town solution to support a few lamps and a 12k BTUs air-conditioner. For all cases, an estimated load curve (kWh) was defined based on the electronics consumers in each house. Our synthesis algorithm was fed with data and costs of forty equipment items from ten different manufacturers of PV systems.

@@

All experiments regarding the verification tools were conducted on an otherwise idle Intel Xeon CPU E5-4617 ($8$-cores) with $2.90$ GHz and $64$ GB of RAM, running Ubuntu $16.04$ LTS $64$-bits. For HOMER Pro, we have used an Intel Core i5-$4210$ ($4$-cores) with $1.7$ GHz and $4$ GB of RAM running Windows 10. The hardware platform was not the same because of the availability of the machines; this has an impact on performance, which is less favorable to HOMER Pro.. We perform the experiments with a predefined time out of $240$ minutes.

%---------------------------------------------------------------------------
\subsection{Results}
%---------------------------------------------------------------------------
%A Table with the details of the results is present on-line\footnote{\url{https://drive.google.com/file/d/1I1Cg4FNz9grMqXHUmOKnd-\_PFmLpmk6m/view?usp=sharing}}.

Concerning the verifiers' comparison, CPAchecker was able to synthesize the optimal sizing in six out of seven case studies (cases $1$ to $6$): CPAchecker produced the results within the time limit, which varied from $2.24$ to $3.92$ hours. Only case study $7$ led to a \textit{time out} result in CPAchecker. The violation (SAT result) indicated in the on-line table\footnote{\url{https://drive.google.com/file/d/1I1Cg4FNz9grMqXHUmOKnd-\_PFmLpmk6m/view?usp=sharing}} is the $assert$ of Line $22$ at Algorithm~\ref{alg:verification-algorithm}. CBMC and ESBMC are unable to produce any conclusive results since \textit{time-outs} or \textit{memory-outs} occurred; these results partially answer the \textit{EG1} and \textit{EG2}, because there exist optimal solutions for these case studies and CPAchecker presented the best results among the verifiers.

@@

For the inverters, HOMER Pro suggests a value in kW very close to the peak of every case study, and it is just a reference value and not a commercial value of the employed inverter. The proposed synthesis tool, however, presents inverters that are commercial and can be found off-the-shelf. Therefore, this feature is a PRO to the formal synthesis method. Concerning the charge controllers, HOMER Pro does not include it as an explicit equipment in its mathematical model, only the synthesis tool presents a commercial controller and includes it during the cost analysis. Therefore, the formal synthesis method presents more reliable results than HOMER Pro. Case study $7$ was not solved by the synthesis tool within the time limit established during the experimental phase. HOME Pro was unable to simulate case study $3$ since it does not have the feature of adjusting the battery autonomy, i.e., the tool always tries to feed with electricity the given load during $365$ days/year. This lack of recourse is a limitation since it is usual to establish autonomy as a design requirement.

In terms of performance, HOMER Pro was able to evaluate six case studies (cases $1$, $2$, $4$, $5$, $6$, and $7$) within a time shorter than $30$ seconds, which was faster than the proposed synthesis approach (cf.~\textit{EG3}) but not sound as our method.  
Comparing the results between the formal synthesis with CPAchecker and HOMER Pro, we have observed that the cost was very close in cases $1$, $4$, $5$ and $6$, with difference varying from $0.23$\% to $17.4$\%. However, HOMER Pro does not use costs related to charge controllers, which were introduced into our synthesis model. This charge controller cost makes the synthesis approach more precise and real. We observed that there exists a divergence in case study $2$, where the costs presented by HOMER Pro were $54$\% higher than our synthesis tool. However, this case study does not have a deployed PV system in order to validate which result is correct.

@@

%------------------------------------
\section{Conclusion} 
%------------------------------------

Our novelty relies on a practical approach to pursuit the optimal solution of PV systems using formal methods. The use of formal synthesis has no precedent in literature, and we show that the results of our approach, using seven case studies, are promising.
Our synthesis tool can present a solution, which is far detailed and closer to the commercial reality than the solution presented by HOMER Pro, an state-of-the art simulation tool. The use of data from real deployed systems in Amazonas State, Brazil, were important in order to reach that conclusion. The battery autonomy feature of our synthesis approach is an advantage as well. In addition, our automated synthesis method can provide all the details of every component of a PV system solution, with complete electrical details from datasheet of manufacturers, including the model of the component, nominal current, and voltage. These details are important for the owner of the system and aids the process of equipment purchase.
%
% ---- Bibliography ----
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%
\bibliographystyle{splncs04}
\bibliography{trindadeThesis}
%
\end{document}
%\subsection{Design and Simulation of Solar PV systems}
%The design and validation of a PV system can be done by hand or with the aid of a software tool. In order to address different aspects of the PV system design, there are various software tools available in the literature~\cite{Rajanna,Rawat}.
%public domain and commercial software available for the PV market. 
%According to \cite{Brooks}, t
%%%%%%%%%%
%
%The capabilities of tools available in the literature range from simple solar resource and %energy production estimation, %to site survey and system design tools,
%to complex financial analysis and project optimization. At this study, the commercial simulation tool HOMER PRO was selected to be used at the case studies in order to be compared with the automated verification tools.
